\documentclass[letterpaper]{article}
\usepackage{amsmath, amssymb, amsfonts, amsthm, mathtools}
\usepackage[parfill]{parskip}
\usepackage{listings}
\usepackage{xcolor}
\definecolor{wasteOfTime1}{RGB}{128,0,0}
\definecolor{wasteOfTime2}{RGB}{96,64,32}
\usepackage{hyperref}
\usepackage{url}
\usepackage{graphicx}
\usepackage{ragged2e}

\title{Smells Like Teen Spirit}
\author{Nirvana}
\date{1991}
\begin{document}
\maketitle
And I forget just why I taste, oh yeah, I guess it makes me smile.\\
I find it hard, it’s hard to find,
\begin{FlushRight}
	\emph{Oh well, whatever,}\\
	\emph{nevermind.}
\end{FlushRight}
\vspace{3em}
\textbf{Hello, hello, hello, how low\\
Hello, hello, hello, how low\\
Hello, hello, hello, how low\\
Hello, hello, hello}

\vspace{3em}

\textbf{\emph{With the lights out it’s less \textcolor{red}{dangerous},\\
Here we are now, entertain us,\\
\textcolor{wasteOfTime1}{I feel stupid and contagious,}\\
Here we are now, entertain us!}}
\vspace{2em}

\null\hspace{8em}\textbf{A \textcolor{wasteOfTime2}{\underline{mulatto}}! An \textcolor{black!30}{\underline{albino!}} A \underline{mosquito}! \textcolor{violet}{My libido!}}

\vspace{3em}

\begin{center}
	{\sc 
	\large{A denial! A denial! A denial!}

	\vspace{1em}

	\LARGE{A denial! A denial! A denial!}

	\vspace{1em}

	\huge{A denial! A denial! A denial!}}
\end{center}
\newpage
\textbf{Name} Param Rathour. `Param' means `The Best', also name of Supercomputer\\[5pt]
\textbf{Department} Electrical Engineering\\[5pt]
\textbf{Music} \\[5pt]Here are some of my favourite pieces of music!
\begin{itemize}
	\item \href{https://youtu.be/o-ONVkhJVSA}{G Minor Bach (Arr. Luo Ni)}
	\item \href{https://youtu.be/HEf_xrgmuRI}{The Wolf And The Moon by BrunuhVille} 
	\item \href{https://youtu.be/q43wzP6A1CM?list=PL_oWkLvcB4HP1U_mOahMiEqRRKntuRI6Z}{Kingdom of Predators} 
	\item \href{https://youtu.be/Z4R42NALDy8?list=PL_oWkLvcB4HP1U_mOahMiEqRRKntuRI6Z}{To Give a Marionette Life} 
	\item \href{https://youtu.be/l2kwie-gs2o}{Trisha's Lullaby} 
\end{itemize}
Songs
\begin{itemize}
\item \href{https://youtu.be/zABLecsR5UE}{Someone You Loved (Lewis Capaldi)}
\item \href{https://youtu.be/RgKAFK5djSk}{See You Again (Wiz Khalifa)}
\item \href{https://youtu.be/pIBoAh4OXhQ}{Janam Janam (Arijit Singh, Antara Mitra)}
\item \href{https://youtu.be/jo6iAkSoraY}{Tere Liye (Lata Mangeshkar, Roopkumar Rathod)}
\end{itemize}
\paragraph{P.S.} I have learnt \LaTeX\ before from \href{https://www.latex-tutorial.com/tutorials/}{here}, but I took this course as fun and to polish my knowledge.\\
You can take a look at my SOS report \href{https://github.com/paramrathour/Nonlinear-Dynamics/blob/master/Nonlinear%20Dynamics.pdf}{here}.
\end{document}